% resume.tex
% vim:set ft=tex spell:

\documentclass[10pt,a4paper]{article}
\usepackage[a4paper,margin=0.55in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{mdwlist}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{tgpagella}
\pagestyle{empty}
\setlength{\tabcolsep}{0em}

\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=cyan,
		pdfauthor={Rob Brown},
    pdftitle={Rob Brown - Technology Leader - Curriculum Vitae},
		pdfsubject={Work History and Experience of Rob Brown},
		pdfkeywords={CV, Résumé, Work History, Rob Brown},
    % pdfpagemode=FullScreen,
    }

% indentsection style, used for sections that aren't already in lists
% that need indentation to the level of all text in the document
\newenvironment{indentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{#1}}%
	\item[]%
}
{\end{list}}

% opposite of above; bump a section back toward the left margin
\newenvironment{unindentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{-0.5#1}}%
	\item[]%
}
{\end{list}}

% format two pieces of text, one left aligned and one right aligned
\newcommand{\headerrow}[2]
{\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
	#1 &
	#2 \\
\end{tabular*}}

% make "C++" look pretty when used in text by touching up the plus signs
\newcommand{\CPP}
{C\nolinebreak[4]\hspace{-.05em}\raisebox{.22ex}{\footnotesize\bf ++}}

% and the actual content starts here
\begin{document}

\begin{center}
{\LARGE \textbf{Rob Brown}}

robert.will.brown@gmail.com\ \ \textbullet\ \ London \ \textbullet\ \ +44 (0) 7796 711 979
\\
\href{https://robert-will-brown.github.io}{Work \& Project Portfolio}\ \ \textbullet\ \ \href{https://www.linkedin.com/in/robert-w-brown/}{LinkedIn Profile}
\end{center}

\hrule
\vspace{-0.4em}
\subsection*{Experience}

\begin{itemize}
	\parskip=0.1em

	\item
	\headerrow
		{\textbf{Ostmodern}}
		{\textbf{London, UK}}
	\\
	\headerrow
		{\emph{Chief Technology Officer}}
		{\emph{2020 -- Present}}
	\begin{itemize*}
		\item Lead a team of \textasciitilde25 responsible for all Projects and Operations.
		\item Oversee the delivery of projects into Sky New Zealand, The Royal Opera House, Rakuten, F1.
		\item Restructured, modernised and aligned the team. Stripped out old methodologies and tech, introduced Scrum, SRE, DevOps, Chaos Testing, and Serverless improving speed of feature development and improving reliability of running services.
    \item Repositioned product as SAAS from an on-prem deployment model whilst migrating from containers to Serverless.
		\item Improved team culture by implementing automated team health checks and Westrum Organisational Culture scoring to identify areas to improve.  Built a well balanced, friendly and effective team that practices open and transparent communication with the business.
		\item Evolved the overly-complex product into a fast to deploy, well operated service. Went from 1 deployment every 3 months to 10+ a day, with deployment times reduced from weeks to 2 hours.
		\item Reduced AWS bill by >50\% by utilising tooling to gain insight to reduce the size of cloud resources.
		\item Implemented good operational practice e.g., monitoring and alerting, run-books, service catalogs, on-call escalation processes, continuous integration and deployment.  Improved incident resolution and decreased customer outages.
		\item Migrated self-hosted services and tools to SAAS counterparts allowing the team to focus on product development and increasing speed of feature development.
		\item Moved the ownership of infrastructure to the product teams using infrastructure as code, choosing SAAS hosted services and automation.  This reduced the bottlenecks on the infrastructure team and allowed them to reduce by 75\% redeploying them into other areas of the business.
	\end{itemize*}

	\item
	\headerrow
		{\textbf{Visual20}}
		{\textbf{London, Madrid \& Switzerland}}
	\\
	\headerrow
		{\emph{Founder \& Principal Architect}}
		{\emph{2017 -- Present}}
	\begin{itemize*}
		\item Led, designed and delivered complex, international projects using Infrastructure as Code, Chaos Engineering, Ephemeral Environments and Agile.
		\item Led multi national team from Madrid, Switzerland, Bangalore and the UK to successfully build and operate a Video Anti-Piracy platform.  Used thousands of EC2 instances to allow downloading of content from suspected pirate sites.
    \item Built a monitoring service at the UK Home Office using Grafana and Prometheus on AWS to monitor the biometric systems of UK immigration and other UK agencies.
	\end{itemize*}

	\item
	\headerrow
		{\textbf{Friend MTS}}
		{\textbf{London, UK}}
	\\
	\headerrow
		{\emph{Technical Operations Director}}
		{\emph{2015 -- 2017}}
	\begin{itemize*}
		\item Led a team of \textasciitilde45 with ownership of technical, pre-sales, solution architecture and operations.
		\item Integrated services into the Olympics, Sky, BTSport, WWE, Viacom and other MVPDs.
		\item Rebranded company and products to align with the broadcast industry.
		\item Translated complex technical services into easily consumable messages for CXX level customers stream lining the sales process and improving sales pipeline.
		\item Presentations at trade shows (IBC and NAB), allowing audiences to understand the products and their place in the Video ecosystem.
	\end{itemize*}

	\item
	\headerrow
		{\textbf{Irdeto}}
		{\textbf{London, UK}}
	\\
	\headerrow
		{\emph{Senior Solutions Architect}}
		{\emph{2014 -- 2015}}
	\begin{itemize*}
		\item Consulted on the improving the OTT Streaming product allow customer centric features to be developed rather than engineering led features.
		\item Simplified product into an understandable message for non-technical staff and provided internal education enabling the sales teams better chances of selling.
		\item Pitched service to Public broadcasters, MVPDs and streaming services with existing platforms. Representing at industry trade shows.
	\end{itemize*}

	\item
	\headerrow
		{\textbf{Piksel (formerly KIT digital, ioko)}}
		{\textbf{San Diego, CA}}
	\\
	\headerrow
		{\emph{Senior Technical Architect}}
		{\emph{2005 -- 2014}}
		\begin{itemize*}
			\item Archited, built and supported Video streaming platforms for Channel 4, Sky, OSN, AT\&T \& BBC.
			\item Lead Infrastructure Architect for Project Kangaroo a joint venture between BBC, Channel 4 and ITV.
			\item Championed the use of Virtualisation and Cloud to reduce cost and increase agility of projects.
		\end{itemize*}
		\subsection*{\emph{Notable Projects}}
        \begin{itemize}
          \item
          \headerrow
              {\textbf{OSN Play}}
              {\textbf{Dubai}}
              OSN, a satellite broadcaster in the MENA region, wanted to release the regions first video streaming service. I was the Senior Infrastructure Architect and built relationships with the  multi-cultural teams within OSN.  Customer relationship management and troubleshooting of priorty issues.

					\item
          \headerrow
              {\textbf{Channel 4 Television - Streaming Service 4od (now All 4)}}
              {\textbf{London}}
              Channel 4 was the first public broadcaster to launch a streaming service in the UK.  I designed and built infrastructure including Storage, DRM, Transcode Farms, Database, Networks, Firewalls and Load balancers. Undertook root cause analysis of content preparation and site availability issues.  Built and integrated tools to monitor the service for performance and availability.

					\item
          \headerrow
              {\textbf{SeeSaw.com / Project Kangaroo}}
              {\textbf{London}}
              Kangaroo was the working title for a proposed streaming video service offering content from, and owned by, the BBC, ITV and Channel 4. Ran the Infrastructure teams responsible for Architecture \& Operations. Developed processes to onboard and integrate BBC, ITV and Channel 4 to receive content and metadata. Integrated with CDNs, built transcode farm and workflow. Implemented service monitoring platform to track availability and responsiveness metrics.  Presentations to audiences of 150+ engineers on the architecture.

					\item
          \headerrow
              {\textbf{Disney}}
              {\textbf{Florida}}
              Worked on the development of the Magic Band for Disney Parks \& Resorts.

					\item
          \headerrow
              {\textbf{BBC Monitoring}}
              {\textbf{UK}}
              BBC Monitoring is a commercial arm of the BBC, providing signal intelligence across various data sources.

				\item
				\headerrow
						{\textbf{Sky TV - New Online Platform}}
						{\textbf{London}}
						With a team of software architects I designed and built the Sky TV New Online Platform.  Architected, procured and oversaw the physical kit installs.  Built and ran the platform.

			\end{itemize}

	\item
	\headerrow
		{\textbf{Sky}}
		{\textbf{London, UK}}
	\\
	\headerrow
		{\emph{Senior Technical Architect}}
		{\emph{2003 -- 2004}}
	\begin{itemize*}
		\item Provided architecture, technical and project management expertise to strategic technology projects.

	\end{itemize*}

	\item
	\headerrow
		{\textbf{J.P. Morgan}}
		{\textbf{London, UK}}
	\\
	\headerrow
		{\emph{UNIX System Administrator}}
		{\emph{2001 -- 2003}}

	\item
	\headerrow
		{\textbf{Sky}}
		{\textbf{London, UK}}
	\\
	\headerrow
		{\emph{Internet Services Support Supervisor}}
		{\emph{2000 -- 2001}}

	\item
	\headerrow
		{\textbf{Sun Microsystems}}
		{\textbf{London, UK}}
	\\
	\headerrow
		{\emph{Storage Engineer}}
		{\emph{1998 -- 2000}}
\end{itemize}


\hrule
\vspace{-0.4em}
\subsection*{Skills}

\begin{indentsection}{\parindent}
\hyphenpenalty=1000
\begin{description*}
		\item[Business:]
		Technology and Business Leadership, Organisational Growth, Building Effective Teams, Public Speaking, Product Management, Product Development, Team Development, Time-critical project delivery, Relationship Management.
    \item[Personnal:]
		Passionate Technologist, Pragmatic, Results-oriented, Ability to work well under pressure, Flexible, Effective Communicator.
\end{description*}
\end{indentsection}

\hrule
\vspace{-0.4em}
\subsection*{TV \& Media Expertise}

\begin{indentsection}{\parindent}
\hyphenpenalty=1000
\begin{description*}
	\item[Experienced with:]
	Streaming video services, MVPDs, Video metadata, Video assets and asset workflow, Digital content distribution, Technical partner management, Streaming video playback authorisation and authentication, DRM, Video and Film Industry standard specifications, Digital media workflows, VOD, OTT, Anti-Piracy Technologies, Broadcast, Encoding.

\end{description*}
\end{indentsection}

\hrule
\vspace{-0.4em}
\subsection*{Technology Expertise}

\begin{indentsection}{\parindent}
\hyphenpenalty=1000
\begin{description*}
	\item[Technologies:]
	AWS, UNIX / Linux, Storage, Scripting \& Automation, Prometheus, Grafana, \LaTeX, Containers, Shell Sripting, Ansible, Docker, CloudFormation, CDN's, HLS.
	\item[Methodologies:]
	DevOps, Site Reliability Engineering (SRE), Infrastructure as Code, Ephemeral Environments, Chaos Engineering, Cloud Design Patterns, Agile, Scrum, Kanban, ITIL, Continuous Delivery, Continuous Integration, Root Cause Analysis (RCA), Analytical Troubleshooting.
	\item[Skills:]
	Architecture, Design \& Implementation, Cloud, AWS Certified (Lapsed), RHCE (Lapsed), Certified Solaris Admin, High-Availability Infrastructure, Service \& Systems Management, Operations, Monitoring, Kepnor \& Trego trained Analytical Troubleshooting.
\end{description*}
\end{indentsection}


\hrule
\vspace{-0.4em}

\begin{description*}
  	\item
  \headerrow
    {{\textsubscript{Written in \LaTeX, using `vi`. Github actions generate this PDF automatically. Look \href{https://github.com/robert-will-brown/cv}{here} for more details.}}}
    {{\textsubscript{@@version@@}}}

\end{description*}

\end{document}
